Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
Pass on abstract

\begin{abstract}
  Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research.
  The prediction task may be given as a target loss, as in problems like classification or structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
  Techniques to design and analyze surrogate losses in these scenarios seem differ
Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central\jessiet{a tad dramatic?} importance, we give a new technique for constructing lower bounds on the convex prediction dimension that applies to both frameworks. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

>>>>

\begin{abstract}
  Given a prediction task, it is crucial to understand when one can and cannot design an ``efficient'' consistent convex surrogate loss.
  The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
  Techniques to design and analyze surrogate losses in these scenarios are typically studied by different frameworks.%: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
We unify these settings by generalizing notions of consistency from machine learning and give lower bounds on prediction dimension that extend across settings.
Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance, entropy, and norms of the conditional distribution, and resolves stated open problems in the literature.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}
